Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
nudge

By assuming bit-vector semantics to be identical to integer semantics, these
techniques ignore the wrap-around behaviour caused by overflows, which can
be unsound.  In Section~\ref{sec:motivation}, we show that integers and
bit-vectors exhibit incomparable behaviours with respect to termination,
i.e.~ programs that terminate for integers may \emph{not} terminate for
bit-vectors and vice versa.  Thus, abstracting bit-vectors with integers may
give rise to {\em unsound} and {\em incomplete} analyses.

>>>>

By assuming bit-vector semantics to be identical to integer semantics, these
techniques ignore the wrap-around behaviour caused by overflows, which can
be unsound.  In Section~\ref{sec:motivation}, we show that integers and
bit-vectors exhibit incomparable behaviours with respect to termination,
i.e.~programs that terminate for integers need \emph{not} terminate for
bit-vectors and vice versa.  Thus, abstracting bit-vectors with integers may
give rise to {\em unsound} and {\em incomplete} analyses.
